Security Metrics for the Android Ecosystem

### 2015-07-27 spsm04-thomas.tex
Add a parent section on data

\section{Critical vulnerabilities}\label{sec:avo}
We have used data on critical vulnerabilities in Android from AndroidVulnerabilities.org (\avo)~\cite{androidvulnerabilities.org}.
It contains information on the discovery and publication dates, the versions affected and which versions contained fixes.
It only contains critical vulnerabilities such as root vulnerabilities that did not require USB debugging to exploit.
If malicious code exploits a critical vulnerability then it gains control of the device.

@@

\section{Device Analyzer data}\label{sec:da}

>>>>

\section{Data}
We use two sources of data to measure the security of Android: (1) information on the distribution of Android versions over time and (2) information on the critical vulnerabilities found to affect Android.
These two datasets can then be combined to determine the proportion of devices at risk of attack from specific vulnerabilities.

\subsection{Critical vulnerabilities}\label{sec:avo}
We have used data on critical vulnerabilities in Android from AndroidVulnerabilities.org (\avo)~\cite{androidvulnerabilities.org}.
It contains information on the discovery and publication dates, the versions affected and which versions contained fixes.
It only contains critical vulnerabilities such as root vulnerabilities that did not require USB debugging to exploit.
If malicious code exploits a critical vulnerability then it gains control of the device.

@@

\subsection{Device Analyzer data}\label{sec:da}
